\LARGE Coursework \\ Module Name (CMM536)

### 2018-04-27 submission.tex
final submission

\subsection{Text Classification}
Most of the preprocessing for text classification is performed within the functions defined earlier. First we create a document-term matrix from all the tweets. We only consider words with a minimum frequency of 10. This removes a significant amount of data, since only 87 unique words are considered.
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #transpose the dtm to get word count for each tweet
> dtm<-make_tdm(df$text,10)
> dtm<-dtm$dtm
> #checknumber of columns used for model
> ncol(as.matrix(dtm))
\end{Sinput}
\begin{Soutput}
[1] 87
\end{Soutput}
\end{Schunk}
\hspace{1cm} 
Using the RTextTools package, the tweets are saved in a container-type object. This automatically performs a train-test split. In this case the training set forms 70\% of the data:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> container <- create_container(dtm, df$label,trainSize=1:round(0.7*nrow(df)),
+	 testSize=(round(0.7*nrow(df))+1):nrow(df),virgin=TRUE)
> 
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
A number of classification models are trained on the data, and evaluated on the test set. RTextTools automatically creates results objects which we can use to evaluate model performance:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #train some models and analyse the results
>set.seed(57)
> models <- train_models(container,algorithms=c("SVM","BAGGING","BOOSTING","RF"))
> results <- classify_models(container, models) #can use for conf matrix

\end{Sinput}
\end{Schunk}
\hspace{1cm} 
Looking at confusion matrices for each of the model types we get the following:

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> print("SVM")
\end{Sinput}
\begin{Soutput}
[1] "SVM"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$SVM_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    379    270
   Remain    15     21
\end{Soutput}
\begin{Sinput}
> print("Bagging")
\end{Sinput}
\begin{Soutput}
[1] "Bagging"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$BAGGING_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    100     41
   Remain   294    250
\end{Soutput}
\begin{Sinput}
> print("Boosting")
\end{Sinput}
\begin{Soutput}
[1] "Boosting"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$LOGITBOOST_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    383    272
   Remain    11     19
\end{Soutput}
\begin{Sinput}
> print("Random Forest")
\end{Sinput}
\begin{Soutput}
[1] "Random Forest"
\end{Soutput}
\begin{Sinput}
> table(predicted=results$FORESTS_LABEL,actual=container@testing_codes)
\end{Sinput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    105     44
   Remain   289    247
\end{Soutput}
\end{Schunk}

>>>>

\subsection{Text Classification}
Most of the preprocessing for text classification is performed within the functions defined earlier. First we create a document-term matrix from all the tweets. We only consider words with a minimum frequency of 10. This removes a significant amount of data, since only 87 unique words are considered.
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}

> #transpose the dtm to get word count for each tweet
> dtm<-make_tdm(df$text,10)
> dtm<-dtm$dtm
> #checknumber of columns used for model
> ncol(as.matrix(dtm))
\end{Sinput}
\begin{Soutput}
[1] 87
\end{Soutput}
\end{Schunk}
\hspace{1cm} 
Using the RTextTools package, the tweets are saved in a container-type object. This automatically performs a train-test split. In this case the training set forms 70\% of the data:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> container <- create_container(dtm, df$label,trainSize=1:round(0.7*nrow(df)),
+	 testSize=(round(0.7*nrow(df))+1):nrow(df),virgin=TRUE)
> 
\end{Sinput}
\end{Schunk}
\hspace{1cm} 
A number of classification models are trained on the data, and evaluated on the test set. RTextTools automatically creates results objects which we can use to evaluate model performance:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}
> #train some models and analyse the results
>set.seed(57)
> models <- train_models(container,algorithms=c("SVM","BAGGING","BOOSTING","RF"))
> results <- classify_models(container, models) #can use for conf matrix

\end{Sinput}
\end{Schunk}
\hspace{1cm} 
Looking at confusion matrices for each of the model types we get the following:
\hspace{1cm} 
\begin{Schunk}
\begin{Sinput}

> table(predicted=results$SVM_LABEL,actual=container@testing_codes)
> table(predicted=results$BAGGING_LABEL,actual=container@testing_codes)
> table(predicted=results$LOGITBOOST_LABEL,actual=container@testing_codes)
> table(predicted=results$FORESTS_LABEL,actual=container@testing_codes)
\end{Sinput}
\end{Schunk}

\begin{figure}[H]
\begin{center}
\begin{Schunk}

\begin{Soutput}
[1] "SVM"
\end{Soutput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    379    270
   Remain    15     21
\end{Soutput}

\begin{Soutput}
[1] "Bagging"
\end{Soutput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    100     41
   Remain   294    250
\end{Soutput}
\begin{Soutput}
[1] "Boosting"
\end{Soutput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    383    272
   Remain    11     19
\end{Soutput}
\begin{Soutput}
[1] "Random Forest"
\end{Soutput}
\begin{Soutput}
         actual
predicted Leave Remain
   Leave    105     44
   Remain   289    247
\end{Soutput}
\end{Schunk}
